\chapter{BACKGROUND STUDY AND LITERATURE REVIEW}

\section{Background study}
"Mitho Delivery" is an innovative and responsive online food delivery website that delivers to both restaurants and customers, enhancing the way people experience dining and food ordering. Through its user-friendly interface, the platform offers a seamless and efficient solution for individuals seeking culinary delights from a variety of local restaurants delivered right to their doorsteps.By embracing the digital realm, "Mitho Delivery" empowers users to effortlessly navigate a wide array of cuisines and menus. This virtual approach eliminates the inconvenience of traditional methods such as physical menus and phone orders. Instead, customers can browse and select dishes with just a few clicks, saving them valuable time and effort.This project isn't solely about technology; it's about changing the way people interact with food. With a robust network of partner restaurants and a well-established logistics system, "Mitho Delivery" provides a comprehensive solution for hassle-free dining in Nepal. This solution doesn't just connect customers with restaurants; it bridges the gap between cravings and fulfillment, all within the comfort of homes or offices.
The platform's diverse selection of restaurants, ranging from local gems to globally recognized chains, grants customers an unparalleled variety of choices to satisfy their culinary desires. Through the platform's intuitive design, customers can explore menus and seamlessly place orders that reflect their unique tastes. Beyond convenience, "Mitho Delivery" has the potential to drive growth within the Nepalese restaurant industry by expanding restaurants' reach and amplifying their revenue streams.As the project expands and becomes a driving force in the dining landscape, it doesn't merely reshape consumer habits but also empowers local restaurants to engage with a broader customer base. This mutual benefit fosters a positive ecosystem, boosting customer satisfaction while simultaneously driving growth for restaurant partners.
\\\\
In essence, "Mitho Delivery" isn't just a website; it's a game-changer that transcends the conventional food ordering experience. By providing accessibility, convenience, and enjoyment, the project redefine the way Nepalese individuals and families enjoy their meals while contributing to the evolution of the restaurant industry. Through technology-driven efficiency, the project creates a harmonious relationship between customers and restaurants, setting the stage for a revolutionary dining transformation in Nepal and beyond.

\section{Literature review}
The advancement of technology has revolutionized the way we order food, giving rise to the phenomenon of online meal ordering systems. This approach offers a swift and efficient way to order food via the internet, simplifying the process down to a single click. In the traditional scenario, consumers would physically visit restaurants, select their meals, and make payments on a daily basis. However, the availability of online ordering brings an added layer of convenience and choice.

The concept of online meal ordering has expanded the options available to customers. While some eateries allow patrons to place orders ahead of time for pickup or delivery, certain limitations exist. Availability of specific items and the inability to personalize orders can sometimes hinder the dining experience, preventing customers from accessing the full variety they desire.

Domino's Pizza is the world's second-largest pizza company with 9,436 stores globally, 95 percent of which are franchised. Domino's franchisees in the U.S. market were able to purchase fresh dough, cheese, pizza toppings, and other menu ingredients and store supplies directly from the company-owned supply chain system. When commodity prices became more volatile in 2007 and 2008, executives at Domino's changed the way they worked with suppliers and franchisees to manage costs and risks, and better leverage the assets of the supply chain system. As the company prepared to accelerate international growth in 2011 and beyond, executives contemplated how to best apply their purchasing and supply chain knowledge into new international markets \cite{bell2012domino}.

In todays digital age, people rely on the internet for food orders, often leaving online reviews.
Our project focuses on analyzing sentiment in Bangla food reviews. Since there was no existing
Bangla dataset, we collected over a thousand food reviews from platforms like Foodpanda,
Hungrynaki, Shohoz food, and Pathao food. After labeling and preprocessing the data, we used
machine learning and deep learning models.This research can help the food industry
understand Bangla food review sentiment, benefiting their decision-making process\cite{junaid2022bangla}.

Research conducted on this subject delves into the impact of convenience, security, and delivery on online shopping behavior for food. Data collected from a questionnaire involving 250 online food shoppers in Kathmandu Valley revealed that convenience and security play a significant role in influencing online shopping behavior, while the effect of delivery is comparatively weaker. This study underscores the vital role these factors play in shaping consumer behavior when it comes to online food shopping \cite{manandhar19online}.

Zomato started in 2008 underneath the name, ‘Foodiebay’ to begin with. Later in 2010, it had been renamed to ‘Zomato’. Constantly 2011, Zomato extended to increasingly urban regions the country over in Mumbai, Delhi NCR, Chennai, Bangalore, Kolkata and Pune. After that in the year 2012, the corporate extended working all around in various countries like the UAE, Qatar, Sri Lanka, UK, South Africa and Philippines. In the year 2013, Zomato had moved their organizations in Brazil, New Zealand, Turkey and Indonesia, with its applications and site open in various lingos isolated from English. After that in April 2014, Zomato impelled its organizations in Portugal Republic, trailed by Canada, Lebanon and Ireland around a similar time. The acquiring of Settled - based sustenance zone ‘Urban spoon’ signified the organization’s passageway into the United States, Canada and Australia, and conveyed it into direct test with ‘Wail’, ‘Zagat' and ‘Open Table’. With the introduction of .xxx zones in 2011, Zomato also impelled ‘zomato.xxx’, a site dedicated to finding spot to eat near to your territory. It later moved a print adjustment of the site substance named, ‘Citibank Zomato Restaurant Guide’, got together with Citibank in May 2012, at any rate later it was halted \cite{panigrahi2020case}.

Online food ordering and delivery services have gained widespread popularity due to the ubiquity of smartphones and the internet. DoorDash, for instance, has embraced this trend, and an analysis using Michael Porter's five-force model indicates that it faces intense competition from both established competitors and substitutes. Meanwhile, the influence of suppliers is growing. Although the threat of new entrants is low, and buyers in American suburban areas exhibit limited bargaining power, DoorDash's position remains dynamic and competitive \cite{zhang2021qualitative}.





