%==============================Abstract Page=================================================
\chapter*{\centerline{ABSTRACT}}
\addcontentsline{toc}{chapter}{ABSTRACT}
\thispagestyle{plain} 
% Abstract (200 to 250 Words)
\vspace{-0.5cm}
The focus of our project is on the growth of the IT sector in Nepal, specifically within the food domain. A website for food ordering is being developed to address potential technical challenges. To overcome these challenges, necessary resources and references to relevant projects will be utilized. The adoption of the RAD model will serve as a framework for efficient project management.The primary objective of this project is to create a functional website that minimizes the occurrence of bugs. This website will become a valuable resource in the future, characterized by its user-friendly interface and seamless ordering process. The overall customer experience will be enhanced as a result.It is firmly believed that this project will contribute to the advancement and development of the community. The potential to revolutionize the food ordering process in Nepal is significant, offering increased convenience and accessibility. Moreover, confidence exists that this project will act as an inspiration to the younger generation, motivating them to pursue further innovations and advancements within the realm of IT.In summary, the project's goal is to utilize technology to enhance the food industry in Nepal. The creation of an efficient and user-friendly website is envisioned to have positive impacts on both the community and the younger generation, thereby fostering further development and innovation within our society.


\par
\textbf{Keywords:} \textit{Convenience, Food Industry, Innovation} 
%=============================================================================================
% (a) Inclusion of three to four Keywords (Lexicographical Order)
\newpage